Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.

### 2020-10-10 results.tex
complete results + add conclusion

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/spectrum}
 \caption{Amplitude spectral density of the GW detectors advanced LIGO (aLIGO) and Advanced Virgo (ADV) at design sensitivity and of the proposed third generation detectors Cosmic Explorer and Einstein Telescope. Eintein Telescope sensitivity curve ET-B is obtained pushing second generation detector technology at its limit. ET-C and ET-D sensitivity curves correspond to a detector configuration where a low-power cryogenic low-frequency interferometer and a high-power room temperature high-frequency interferometer are sharing the same infrastructure~\cite{Hild_20211}. Cosmic Explorer design sensitivity will be achieved in two stages. Stage 1 (CE1) is expected to use the technology developed for the “A+” upgrade to advanced LIGO but scaled up to a 40 km detector while stage 2 (CE2) will implement state-of-the-art technology to decrease quantum and thermal noises~\cite{reitze2019cosmic}. } \label{fig:spectrum}
\end{figure}

@@

Figure \ref{fig:s20--SFHo_all3G} shows $\Delta$ as function of the source distance for {\tt s20.0--SFHo}
waveform for the 5 3G detectors configurations. Overall, the ratio is well reconstructed up to distances
in the range \unit{100--200}[kpc] which represents an improved of at least a factor 10 with respect to
advanced LIGO and advanced Virgo detectors. We can also note that the Einstein Telescope results lay in
between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\tt s25.0-LS220}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather incertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather large range obtained
for the different waveforms probing a large range of progenitor masses.

\mab{add comment on the mass progenitor dependence}\\
\mab{say that the main depend is the SNR as shown by ddet}

>>>>

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/spectrum}
 \caption{Amplitude spectral density of the GW detectors advanced LIGO (aLIGO) and Advanced Virgo (ADV) at design sensitivity and of the proposed third generation detectors Cosmic Explorer and Einstein Telescope. Eintein Telescope sensitivity curve ET-B is obtained pushing second generation detector technology at its limit. ET-C and ET-D sensitivity curves correspond to a detector configuration where a low-power cryogenic low-frequency interferometer and a high-power room temperature high-frequency interferometer are sharing the same infrastructure~\cite{Hild_2011}. Cosmic Explorer design sensitivity will be achieved in two stages. Stage 1 (CE1) is expected to use the technology developed for the “A+” upgrade to advanced LIGO but scaled up to a 40 km detector while stage 2 (CE2) will implement state-of-the-art technology to decrease quantum and thermal noises~\cite{reitze2019cosmic}. } \label{fig:spectrum}
\end{figure}

@@

Figure \ref{fig:s20--SFHo_all3G} shows $\Delta$ as function of the source distance for {\tt s20.0--SFHo}
waveform for the 5 3G detectors configurations. Overall, the ratio is well reconstructed up to distances
in the range \unit{100--200}[kpc] which represents an improved of at least a factor 10 with respect to
advanced LIGO and advanced Virgo detectors. We can also note that the Einstein Telescope results lay in
between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\tt s25.0-LS220}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather incertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather wide range obtained
for the different waveforms probing a large range of progenitor masses.
We did not find any correlation between the mass of the progenitor and $d_r$. On the other hand, the quality
of the ratio reconstruction depends on the signal-to-noise ratio, expressed in Table \ref{tab:results} by
$d_{det}$.
